\documentclass[letterpaper,10pt,titlepage]{article}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\def\name{Jonah Brooks}

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs472 ``computer architecture'' paging},
  pdftitle = {CS 472 Homework \item Paging},
  pdfsubject = {CS 472 Homework 3},
  pdfpagemode = UseNone
}

\begin{document}
Jonah Brooks

CS472 HW3

11/06/15

\begin{enumerate}
\item 
32 bit addressing with 4KB pages require 12 bits for page offset, which leaves
20 bits for the physical page number. Therefore there are 2\textsuperscript{20} entries with 10 bytes
each. This results in 2\textsuperscript{20} * 10 = 10MB of memory.  

\item 
64 bit addressing with 4KB pages require 12 bits for page offset, which leaves
52 bits for the physical page number. Therefore there are 2\textsuperscript{52} entries with 10 bytes
each. This results in 2\textsuperscript{52} * 10 = 40PB of memory.  

\item 
32 bit addressing with 8KB pages require 13 bits for page offset, which leaves
19 bits for the physical page number. Therefore there are 2\textsuperscript{19} entries with 10 bytes
each. This results in 2\textsuperscript{19} * 10 = 5120KB (5.12MB) of memory.  

\item 
64 bit addressing with 8KB pages require 13 bits for page offset, which leaves
51 bits for the physical page number. Therefore there are 2\textsuperscript{51} entries with 10 bytes
each. This results in 2\textsuperscript{51} * 10 = 20PB of memory.  

\item 
Pipelining is the process of allowing multiple operations to execute (in part) at once by each
utilizing different subsections of the pipeline. For instance, one instruction is decoded in the first
clock cycle. In the next clock cycle, that instruction begins the next step of execution while a second
instruction is being fetched and decoded. This is useful because it allows more of the processor to be
used at once, resulting in more instructions being completed per clock cycle (instead of each one 
having to wait for the previous instruction to finish). 

\item
I don't know, and I still have the migraine that kept me from turning this in on time in the first place. 
It's time for Tylenol and a few hours of quietly staring at the inside of my eyelids. 

\item
Pipeline hazards are when something complicates the pipelining system. For instance, if one instruction
requires the output of the one before it, or if two instructions needing to read/write from the same
register at the same time. These can be dealt with by out of order execution or added delays in certain
stages to sync up output between instructions. Other hazards, such as branches in the code rendering
previously partially computer instructions obsolete, can only be partially avoided by branch prediction
or limiting the pipeline depth. 
\end{enumerate}

\end{document}
